Some examples in extended logic counting classes

### 2017-01-09 LICS/syntactic-clo.tex
Acortando el paper.

A natural question at this point is whether the property of being closed under subtraction by one could be generalized to proper subtraction. More precisely, a function complexity class $\CC$ is said to be closed under subtraction if for every $f,g \in \CC$, it holds that $(f \dotdiv g) \in \CC$, where $(f \dotdiv g)(x)$ is defined as $f(x) - g(x)$ if $f(x) \geq g(x)$, and as $0$ otherwise. The following theorem shows that such generalization does not work for any of the function complexity classes considered in this section.
\begin{theorem} \label{sub-pnp}
If any of the classes $\E{1}$, $\QE{1}$ or $\eqso(\logex{1})$ is closed under subtraction, then $\ptime = \np$.
\end{theorem}

>>>>

%A natural question at this point is whether the property of being closed under subtraction by one could be generalized to proper subtraction. More precisely, a function complexity class $\CC$ is said to be closed under subtraction if for every $f,g \in \CC$, it holds that $(f \dotdiv g) \in \CC$, where $(f \dotdiv g)(x)$ is defined as $f(x) - g(x)$ if $f(x) \geq g(x)$, and as $0$ otherwise. The following theorem shows that such generalization does not work for any of the function complexity classes considered in this section.
%\begin{theorem} \label{sub-pnp}
%If any of the classes $\E{1}$, $\QE{1}$ or $\eqso(\logex{1})$ is closed under subtraction, then $\ptime = \np$.
%\end{theorem}
